A Machine Learning Approach to MLB Catcher Framing

### 2021-12-10 Slides.Rmd

\tiny
```{r, echo=FALSE}
load("Model-Outputs/logistic-CM.Rda")
load("Model-Outputs/logistic-error.Rda")

@@

```{r, cache=T}
data_no_catchers <- usable_data[, -18]
x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
y <- data_no_catchers$strike

>>>>

```{r, echo=FALSE}
load("Model-Outputs/logistic-CM.Rda")
load("Model-Outputs/logistic-error.Rda")

@@

```{r}
data_no_catchers <- usable_data[, -18]

x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
y <- data_no_catchers$strike
